---
title: "Getting Started"
author: "Jane Doe"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cbds)
```

This package includes a number of functions helpful to our daily work working with tabular data. While the functionality of this package is currently limited to a few functions, over time, we intend to include additional functions that will help make our work easier!

To demonstrate how to utilize the functionality in this package, we'll use a dataset available from the package `ggplot2`: msleep

# The Data

```{r dataset}
library(ggplot2)
msleep
```

# Missing Data: `check_na()`

`check_na()` is a small function that returns the number of observations in a single variable as well as the number of missing and non-missing variables. It's a quick check on the data.

```{r check-na}
# calculate missingness
check_na(msleep$brainwt)
```

# Custom Plotting: `theme_cbds()`

In data analysis, we often generate a number of plots using `ggplot2`. `theme_cbds` generates a custom theme that we can apply to all of our plots.

For example, if we did not use this custom theme, a plot may look as follows (with `ggplot2` default settings):

```{r default-plot}
ggplot(msleep, aes(sleep_rem, sleep_total)) + geom_point()
```

But, with our custom theme, it would look as follows:

```{r theme-cbds}
ggplot(msleep, aes(sleep_rem, sleep_total)) + 
  geom_point() + 
  theme_cbds()
```

The data themselves don't change, but we've:

- removed the gridlines
- plotted only the x- and y-axis lines
- specified a white background
- moved the tick labels closer to the axes
- removed axis tick marks

Note, that this does not only apply to scatterplots. For example, this theme can be used for any type of `ggplot2` plot:

```{r theme-cbds-barplot}
ggplot(msleep, aes(vore)) + 
  geom_bar() + 
  theme_cbds()
```


